---
title: "Homework 3"
author: "Matt Fry"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Directions
## Write a function in R called GuessTheNumber().  This function will randomly 
## generate an integer between a lower and upper bound (inclusive).  The user 
## will then be prompted to enter in a guess for this number.  If their guess 
## is too high, the function will tell the user the guess was too high and 
## ask for another guess!  When too low, it will tell the user and ask for 
## another guess.  The game continues until the user correctly guesses 
## the random number. 

```{r}
## #Modularization: Getting R to give the user a random number between
##    user specified bounds -- 1:30 as NULL -- and set a seed
GuessTheNumber <- function(lowerBound=1, upperBound=30, seed=NULL){
  if(!is.numeric(lowerBound) || !is.numeric(upperBound)) {
    stop("The lower and upper bounds must be numbers")
  } else if(lowerBound >= upperBound){
    stop("The lower bound must be less than the upper bound")
  } else{
  set.seed(seed)
  randomNum <- sample(lowerBound:upperBound, size=1)
  }
}
```

```{r}
## #Modularization: Allowing R to prompt the user to enter in a guess and
##    tell the user if it is high or low -- Repeat this until the number 
##    is successfully guessed
GuessTheNumber <-function(lowerBound=1, upperBound=30, seed=NULL){
   if(!is.numeric(lowerBound) || !is.numeric(upperBound)) {
    stop("The lower and upper bounds must be numbers")
  } else if(lowerBound >= upperBound){
    stop("The lower bound must be less than the upper bound")
    ## Error checking portion, makes sure the inputs are numbers and the
    ##  lowerBound is less than the upperBound, returns meaningful error
    ##  message when prompted
  } else{
  set.seed(seed)
  RandomNum <- sample(lowerBound:upperBound, size=1)
  NumOfGuesses <- 0
  NewNumber <- c()
  Guess <- as.integer(readline("Guess the Number Within the Bounds: "))
  NewNumber <- c(NewNumber, Guess)
  NumOfGuesses <- NumOfGuesses + 1
  while(Guess != RandomNum) {
    if(Guess < RandomNum){
      Guess <- as.integer(readline("Guess is TOO LOW, try again: "))
    } else{
      Guess <- as.integer(readline("Guess is TOO HIGH, try again: "))
    }
    NumOfGuesses <- NumOfGuesses + 1
    NewNumber <- c(NewNumber, Guess)
    RandomNumber <- c("ANSWER:", RandomNum)
    NumGuesses <- c("Total Guesses:", NumOfGuesses)
    Guesses <- c("Guesses:", NewNumber)
  }
  } 
  list(NumGuesses, RandomNumber, Guesses) ## This is what I want for the final
                                          ##  output so it goes b4 the last bracket
}
```

```{r}
## Making sure my program actually works:
## Had to add another line (line 68) to allow for the original guess to appear
##  in the Final list of guesses
GuessTheNumber()
```

